Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor

### 2020-10-10 docs/paper/paper.tex
* more fixes

We have performed experiments comparing the proposed ANN architecture with the state-of-the-art method proposed in \cite{paper0}. Results of this experiment are demonstrated in Figure \ref{chart:perfnoaug}. In the SPR dataset experiment, ANN models are predicting a new configuration and the number of samples available for training is lower. Therefore, they both have higher error rates compared to the PCF dataset. According to Figure \ref{chart:perfnoaug}c, $n_{analyte} = 1.35$ case, the ANN method proposed in \cite{paper0} does not fit to the curve caused by the change in the wavelength. This can be linked to the fact that this method uses full-batch learning and therefore under-fits the model \cite{keskar2016large}. Regardless of this, both models have similar MSE due to the shift in the curve fit. Since the network is never exposed to this particular geometric configuration shift in the curve fit occurs.

@@

The first set of experiments performed on the GAN phase is the number of the augmented samples. In these experiments, we have augmented the proposed ANN system with a varying number of samples. According to these experiments we have reached the minimum MSE at 1000 samples. Adding further samples slightly reduces the performance while increasing the training time. The results of this experiment is demonstrated in Figure \ref{chart:gansamples}. The number of augmented samples may depend on the dataset that is used. However, in our experiments 1000 augmented samples produce good results in both datasets.

@@

In this paper, we have demonstrated that the use of generative adversarial networks can be beneficial to neural networks that are designed to compute propagation characteristics of PCF devices. Additionally, we have also proposed and demonstrated a neural network that is both more generic and more accurate to estimate the confinement loss compared to the state-of-the-art network. The GAN phase also reduces the required samples to fully train the ANN, reducing the work necessary to employ the proposed system. The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research article. In our experiments, due to optimized dataset the accuracy of the method proposed in Ref. \cite{paper0} is also improved.

>>>>

We have performed experiments comparing the proposed ANN architecture with the state-of-the-art method proposed in \cite{paper0}. Results of this experiment are demonstrated in Figure \ref{chart:perfnoaug}. In the SPR dataset experiment, ANN models are predicting a new configuration and the number of samples available for training is lower. Therefore, they both have higher error rates compared to the PCF dataset. According to Figure \ref{chart:perfnoaug}c, $n_{analyte} = 1.35$ case, the ANN method proposed in \cite{paper0} does not fit to the curve caused by the change in the wavelength. 
%This can be linked to the fact that this method uses full-batch learning and therefore under-fits the model \cite{keskar2016large}.
Regardless of this, both models have similar MSE due to the shift in the curve fit. Since the network is never exposed to this particular geometric configuration shift in the curve fit occurs.

@@

The first set of experiments performed on the GAN phase is the number of the augmented samples. In these experiments, we have augmented the proposed ANN system with a varying number of samples. According to these experiments we have reached the minimum MSE at 1000 samples. Adding further samples slightly reduces the performance while increasing the training time. The results of this experiment is demonstrated in Figure \ref{chart:gansamples} \hl{showing that the increasing number of augmented samples increases the performance to a point where it will start hurting the performance (>3000 samples). The reason behind this augmented samples are not perfect. They deviate from the actual data. However, up to a point, the performance impact of having low number of training samples out-weighs the imperfect data generated by GAN.} The number of augmented samples depends on the training samples that are available and can vary depending on the dataset used.

@@

In this paper, we have demonstrated that the use of generative adversarial networks can be beneficial to neural networks that are designed to compute propagation characteristics of PCF devices. Additionally, we have also proposed and demonstrated a neural network that is both more generic and more accurate to estimate the confinement loss compared to the state-of-the-art network. The GAN phase also reduces the required samples to fully train the ANN, reducing the work necessary to employ the proposed system. The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research article. \hl{The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research; in the experiments, it surpassed the accuracy of the method proposed in }\cite{paper0}\hl{ on the dataset that method is optimized on.}
